%Revised date 
%\documentclass[preprint,prl,aps]{revtex4}
%\documentstyle[prl,aps]{revtex}
%\renewcommand\baselinestretch{1}
%\input epsf
%\setcounter{page}{1}
%\flushbottom
%\usepackage{graphicx}


\documentclass[12pt]{article}
%\usepackage{rotating}
\usepackage{epsfig}


\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{rotating}
\hypersetup{
  colorlinks,
  citecolor = black,
  filecolor = black,
  linkcolor = black,
  urlcolor = black,
  linktocpage
}

\usepackage[usenames]{color}
\topmargin-1.5cm
\oddsidemargin+0.1cm
\textheight23cm
\textwidth16cm
\setcounter{page}{1}
%\flushbottom


\def\SSA{single spin asymmetry}  
\def\SIDIS{semi-inclusive deep-inelastic scattering}  
% A useful Journal macro  
\def\Journal#1#2#3#4{{#1} {\bf #2}, #3 (#4)}  
  
% Some useful journal names  
\def\EPJA{{\em Eur. Phys. J.} A}  
\def\EPJC{{\em Eur. Phys. J.} C}  
\def\NCA{{\em Nuovo Cimento} A}  
\def\NIM{\em Nucl. Instrum. Methods}  
\def\NIMA{{\em Nucl. Instrum. Methods} A}  
\def\NPA{{\em Nucl. Phys.} A}  
\def\NPB{{\em Nucl. Phys.} B}  
\def\PLB{{\em Phys. Lett.}  B}  
\def\PRL{\em Phys. Rev. Lett.}  
\def\PRD{{\em Phys. Rev.} D}  
\def\PRC{{\em Phys. Rev.} C}  
\def\ZPC{{\em Z. Phys.} C}  
\def\PR{{\em Phys. Rep.}}  

\begin{document}
%\draft
%\centerline{}
\title{SoLID Collabration List - Update in April 2015}  
\maketitle 

\begin{center}
\large{J. Arrington, K. Hafidi, P. Reimer, B. Tice} \\
\it{Argonne National Lab, Argonne, IL}
\end{center}

\begin{center}
\large{A. Kolarkar} \\
\it{Boston University, Boston, MA}
\end{center}

\begin{center}
\large{J. Huang, X. Qian} \\
\it{Brookhaven National Laboratory, Upton, NY}
\end{center}

\begin{center}
\large {K. Aniol, D. J. Margaziotis}\\
\it{California State University-Los Angles, Los Angles, CA}
\end{center}

\begin{center}
\large {G. Franklin, B. Quinn}\\
\it{Carnegie Mellon University, Pittsburgh, PA}
\end{center}

\begin{center}
\large {S.Y.~Hu, S.Y.~Jian, X.L.~Li \\  X.M.~Li, H. Liang,
J.~Yuan, J. Zhou, S.H. ~Zhou}\\
\it{China Institute of Atomic Energy, Beijing, P. R.~China}
\end{center}

\begin{center}
\large{D. Armstrong, T. Averett, W. Deconinck, H. Yao}\\
\it{College of William \& Mary, Williamburg, VA}
\end{center}

\begin{center}
\large{C.M. Camacho, F. Itard}\\
\it{LPC Clermont, Universite Blaise Pascal CNRS/IN2P3, F-63177 Aubiere, France}
\end{center}

\begin{center}
\large{L.P. Kaptari}\\
\it{Bogoliubov Laboratory for Theoretical Physics, JINR, Dubna, Russia}
\end{center}

\begin{center}
\large{H. Gao, M. Huang,
 G. Laskaris, X.Q. Li, M. Meziane,
 C. Peng, X. Yan, Z.H. Ye, W. Xiaong, Y. Zhang}\\
\it{Duke University and TUNL, Durham, NC}
\end{center}

\begin{center}
\large{P. Markowitz, L. Guo}\\
\it{Florida International University, Miami, FL}
\end{center}

\begin{center}
\large{A.~Afanasev} \\
\it{George Washington University, Washington, DC}
\end{center}

\begin{center}
\large{C. Chen, N. Kalantarians, E. Christy} \\
\it{Hampton University, Hampton, VA}
\end{center}


\begin{center}
\large{H.P. Cheng, F.J. Jiang, R.C. Liu, H.J. Lu, Y. Shi, X.H. Yan}\\
\it{Huangshan University, Huangshan, P. R. China}
\end{center}

\begin{center}
\large{X.S. Chen, N. Li}\\
\it{Huazhong University of Science and Technology, Wuhan, P. R. China}
\end{center}

\begin{center}
\large{A. Vossen}\\
\it{Indiana University, Bloomington, IN}
\end{center}


\begin{center}
\large{U. D'Alesio, F. Murgia}\\
\it{Cagliari University and INFN, Cagliari Torino, Italy}
\end{center}

\begin{center}
\large{
R.~De~Leo, L.~Lagamba, S.~Marrone, G. Simonetti, I. Vilardi}\\ 
\it{INFN-Bari and University of Bari, Bari, Italy}  
\end{center}

\begin{center}
\large{L. Barion, M. Contalbrigo, C. Giuseppe, P. Lenisa, L. L. Pappalardo
}\\ 
\it{University of Ferrara and INFN Ferrara, Ferrara, Italy}
\end{center}

\begin{center}
\large{M. Aghasyan, A. Courtoy,
 E. De Sanctis, D. Hasch, M. Mirazita,
 S. A. Pereira, \\ S. Pisano, P. Rossi}\\ 
\it{INFN Laboratori Nazionali di Frascati, Frascati, Italy}
\end{center}

\begin{center}
\large{A. Bacchetta, B. Pasquini, M. Radici}\\
\it{INFN, Sezione di Pavia, and University of Pavia, Italy}
\end{center}

\begin{center}
\large{S. Scopetta}\\
\it{University degi Studi di Perguria, INFN, Perugia, Italy}
\end{center}

\begin{center}
\large{E. Pace}\\
\it{Rome-Tor Vergata University, Rome, Italy}
\end{center}

\begin{center}
\large{E.~Cisbani, F.~Cusanno, A. Del Dotto, S.~Frullani, F.~Garibaldi} \\
\it{INFN-Roma gruppo collegato Sanit\'a and Italian National Institute of
Health, Rome, Italy}
\end{center}

\begin{center}
\large{F. Meddi, G. Salme', G. M. Urciuoli} \\
\it{INFN-Roma and Sapienza University of Rome, Rome, Italy}
\end{center}

\begin{center}
\large{M. Capogni} \\
\it{INFN Roma gruppo collegato Sanit\`a and ENEA Casaccia, Rome, Italy}
\end{center}

\begin{center}
\large{M. Anselmino, M. Boglione}\\
\it{Torino University and INFN, Torino, Italy}
\end{center}

\begin{center}
\large{A. Giusa, V. Bellini, F. Mammoliti, F. Noto, C.M. Sutera }\\
\it{INFN - Sezione di Catania, Italy}
\end{center}

\begin{center}
\large{D.Y. Chen, X.R. Chen, J. He, R. Wang, H.R. Yang, P.M. Zhang}\\
\it{Institute of Modern Physics, Lanzhou, China}
\end{center}

\begin{center}
\large{H. Avakian, A.~Camsonne, J.-P.~Chen, E.~Chudakov, S. Covrig, M. M. Dalton, \\
A.~Deur, D. Gaskell, J.~Gomez,  D. W.~Higinbotham, J. O.~Hansen, M.~Jones, \\
C. Keppel, S. Malace, B. Moffit, R.~Michaels, A. Prokudin, Y. Qiang, \\
B. Sawatzky,  B.~Wojtsekhowski}\\
\it{Jefferson Lab, Newport News, VA}
\end{center}

\begin{center}
\large{J. Bericic, M. Mihovilovi\v{c}, S. \v{S}irca, S. Stajner}\\
\it{Jo\v{z}ef Stefan Institute, Liubljana, Slovenia}
\end{center}

\begin{center}
\large {B.T. Hu, Y. Zhang}\\
\it{Lanzhou University, Lanzhou, China}
\end{center}

\begin{center}
\large {A. T. Katramatou, G.G. Petratos}\\
\it{Kent State University, Kent, OH}
\end{center}

\begin{center}
\large{F. Yuan} \\
\it{Lawrence Berkeley National Laboratory, Berkeley, CA}
\end{center}

\begin{center}
\large{T. Holmstrom} \\
\it{Longwood University, Farmville, VA}
\end{center}


\begin{center}
\large{X. Jiang, M.X. Liu}\\
\it{Los Alamos National Laboratory, Los Alamos, NM}
\end{center}

\begin{center}
\large{K. Grimm, K. Johnston, N. Simicevic, S. Wells}\\
\it{Louisiana Tech University, Ruston, LA}
\end{center}

\begin{center}
\large{K. Allada, W. Bertozzi, S. Gilad, S. Kowalski, J. Maxwell, N. Muangma}\\ 
\it{Massachusetts Institute of Technology, Cambridge, MA}  
\end{center}

\begin{center}
\large{J. Dunne, D. Dutta, L. EL Fassi, A. Narayan, L. Ndukum, M. H. Shabestari, A. Subedi, L. Yi}\\ 
\it{Mississippi State University, Starkville, MS}  
\end{center}


\begin{center}
\large{M. Burkardt} \\
\it{New Mexico State University, Las Cruces, NM}
\end{center}

\begin{center}
\large{O. Glamazdin, R. Pomatsalyuk} \\
\it{NSC Kharkov Institute for physics and Technology, Kharkov, Ukraine}
\end{center}


\begin{center}
\large{P.M. King, J. Roche}\\ 
\it{Ohio University, Athens, OH}  
\end{center}
\begin{center}

\large{G. Dodge, C.E. Hyde, L. Weinstein, Z. W. Zhao}\\ 
\it{Old Dominion University, Norfolk, VA}  
\end{center}

\begin{center}
\large {B.-Q. Ma, Y.J. Mao}\\
\it{Peking University, P. R.~China}
\end{center}


\begin{center}
\large{L. Gamberg}\\ 
\it{Pennsylvania State University at Berks, Reading, PA}  
\end{center}

\begin{center}
\large{B. Xiao}\\ 
\it{Central China Normal University, Wuhan, China}  
\end{center}

\begin{center}
\large{P. Decowski}\\ 
\it{Smith College, Northhampton, MA}  
\end{center}

\begin{center}
\large{R.~Gilman, G.~Kumbartzki, \\
  R.~Ransome}\\ 
\it{Rutgers University, Piscataway, NJ}  
\end{center}

\begin{center}
\large{S. Choi, Ho. Kang, Hy. Kang, \\
  B. Lee, Y. Oh}\\
\it{Seoul National University, Seoul, Korea}
\end{center}

\begin{center}
\large{Z.T. Liang, X.T. Huang}\\
\it{Shangdong University, Jinan, China}
\end{center}

\begin{center}
\large{A. J. Sarty}\\   
\it{St. Mary's University, Halifax, Nova Scotia, Canada}
\end{center}

\begin{center}
\large{A. Deshpande, T. Hemmick, K. Kumar, S. Riordan}\\   
\it{Stonybrook University, Stonybrook, NY}
\end{center}

\begin{center}
\large{P. Souder, R. Holmes}\\   
\it{Syracuse University, Syracuse, NY}
\end{center}

\begin{center}
\large{G. Ron, E. Piasetzky}\\
\it{Tel aviv University, Tel Aviv, Israel}
\end{center}

\begin{center}
\large{W. Armstrong, H. Atac, A. Blomberg, D. Flay, E. Fuckey, Z.-E.~Meziani, \\
  M. Paolone, M. Posik, E Schulte, N. Sparveris}\\
\it{Temple University, Philadelphia, PA}
\end{center}

\begin{center}
\large {W.-C. Ding, X. Huang, Y.L. Li, L. Shi, J.-B. Wang, Y. Wang,\\  
Z.G. Xiao, P. Zhuang}\\
\it{Tsinghua University, Beijing, P. R. China}
\end{center}

\begin{center}
\large{H. Matevosyan, A.W. Thomas} \\
\it{CSSM and CoEPP, University of Adelaide, North Tce., Adelaide, SA 5005, Australia}
\end{center}

\begin{center}
\large{J. Erler} \\
\it{Universidad Autonoma de Mexico, 01000 Mecico D.F., Mexico}
\end{center}


\begin{center}
\large{A. Puckett, P. Schweitzer} \\
\it{University of Connecticut, Storrs, CT}
\end{center}

\begin{center}
\large{Lorenzo Zana} \\
\it{University of Edinburgh, Edinburgh EH9 3JZ, Scotland}
\end{center}


\begin{center}
\large{J. Annand, D. Hamilton, D. Ireland, K. Livingston, R. Kaiser, \\
I.J.D. MacGregor, D. Protopopescu, G. Rosner, B. Seitz}\\   
\it{University of Glasgow, Glasgow, Scotland}
\end{center}

\begin{center}
\large{N.~Makins, 
J.-C.~Peng}\\   
\it{University of Illinois, Urbana-Champaign, IL}
\end{center}

\begin{center}
\large{W. Korsch}\\   
\it{University of Kentucky, Lexington, KY}
\end{center}

\begin{center}
\large{E.J. Beise}\\   
\it{University of Maryland, College Park, MD}
\end{center}

\begin{center}
\large{S. Johnston, J. Mammei, L. Mercado, R. Miskimen, J. Wexler}\\   
\it{University of Massachusetts, Amherst, MA}
\end{center}

\begin{center}
\large{T. Badman, S. K. Phillips, K. Slifer, P. Solvignon, R. Zielinski}\\   
\it{University of New Hampshire, Durham, NH}
\end{center}

\begin{center}
\large{L. Gan}\\   
\it{University of North Carolina, Wilmington, NC}
\end{center}


\begin{center}
\large {C. Li, J.B. Liu, S.B. Liu, M. Shao, X.L. Wang, Z.Z. Xu, \\ W.B. Yan, W.H. You,
Y.~Ye, Y.X. Zhao, Q.B. Zheng, Y. Zhou, P.J. Zhu}\\
\it{University of Science and Technology of China, Hefei, P. R. China}
\end{center}

\begin{center}
\large{X.Z. Bai, G. Cates, D. Crabb, D. Day, D. Keller, R. Lindgren,\\
  J. Liu, N. Liyanage, V. Nelyubin, 
  B. Norum,  K. Paschke, P. Peng,\\ O.A. Rondon, V. Sulkosky, A. Tkachenko, W. A. Tobias, J. Zhang, \\ X.C. Zheng} \\   
\it{University of Virginia, Charlottesville, VA}
\end{center}


\begin{center}
\large{J.W. Martin}\\   
\it{University of Winnipeg, Winnipeg, MB R3B 2E9, Canada}
\end{center}

\begin{center}
\large{ M.J. Ramsey-Musolf,}\\   
\it{University of Wisconsin, Madison, WI}
\end{center}

\begin{center}
\large {N. Morgan, M. Pitt}\\
\it{Virginia Tech, Blacksburg, VA}
\end{center}

\begin{center}
\large {F. R. Wesselmann}\\
\it{Xavier University of Louisiana, New Orleans, LA}
\end{center}

\begin{center}
\large\bf{and the HallA Collaboration}
\end{center}


%\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

%\clearpage
%\tableofcontents
%\listoffigures
%\listoftables
%\clearpage


\end{document}




